Manuscript

### 2022-09-09 analysis/manuscript.Rmd
add summ C to output

@@

## Supplementary tables
write.xlsx_wrapper(final_table, file=supplementary_tables_file, sheetName="Supp Table 1 complete_summary", row.names=FALSE)
#write.xlsx_wrapper(AM_result_sig.DT, file=supplementary_tables_file, sheetName="Supp Table 2 BF_sig_same_trait_MR", append=TRUE, row.names=FALSE)
#write.xlsx_wrapper(nominally_sig_sex_differences, file=supplementary_tables_file, sheetName="Supp Table 3 nominally_sig_sex_diff", append=TRUE, row.names=FALSE)
#write.xlsx_wrapper(pheno_corr_pearson_sig.DT, file=supplementary_tables_file, sheetName="Supp Table 4 pheno_binned_corrs", append=TRUE, row.names=FALSE)
#write.xlsx_wrapper(corr_vs_MR_effects_sig_dat, file=supplementary_tables_file, sheetName="Supp Table 5 sig_corr_vs_MR", append = TRUE, row.names=FALSE)
write.xlsx_wrapper(sig_confounders, file=supplementary_tables_file, sheetName="Supp Table 6 sig_confounders", append=TRUE, row.names=FALSE)
write.xlsx_wrapper(paths_summary, file=supplementary_tables_file, sheetName="Supp Table 7 paths_summary", append=TRUE, row.names=FALSE)

>>>>

sig_confounders <- corr_potential_trait_confounders_pos %>% filter(sig_confounder) %>% group_by(outcome_ID) %>%
  arrange(-corr_due_to_confounding) %>%
  mutate(total_potential_confounders = n()) %>%
  dplyr::summarize(description = outcome_description[1],

                   total_potential_confounders = total_potential_confounders[1],
                   potential_confounders = paste0(exposure_description, collapse = "; "), 
                   summ_C = sum(corr_due_to_confounding)) %>%
  dplyr::rename(trait_ID = outcome_ID) %>%
  dplyr::rename(trait_description = description) %>% 
  dplyr::select(trait_description, trait_ID, everything())

@@

## Supplementary tables
write.xlsx_wrapper(final_table, file=supplementary_tables_file, sheetName="Supp Table 1 complete_summary", row.names=FALSE)
#write.xlsx_wrapper(AM_result_sig.DT, file=supplementary_tables_file, sheetName="Supp Table 2 BF_sig_same_trait_MR", append=TRUE, row.names=FALSE)
#write.xlsx_wrapper(nominally_sig_sex_differences, file=supplementary_tables_file, sheetName="Supp Table 3 nominally_sig_sex_diff", append=TRUE, row.names=FALSE)
#write.xlsx_wrapper(pheno_corr_pearson_sig.DT, file=supplementary_tables_file, sheetName="Supp Table 4 pheno_binned_corrs", append=TRUE, row.names=FALSE)
#write.xlsx_wrapper(corr_vs_MR_effects_sig_dat, file=supplementary_tables_file, sheetName="Supp Table 5 sig_corr_vs_MR", append = TRUE, row.names=FALSE)
write.xlsx_wrapper(sig_confounders, file=supplementary_tables_file, sheetName="Supp Table 3 sig_confounders", append=TRUE, row.names=FALSE)
write.xlsx_wrapper(paths_summary, file=supplementary_tables_file, sheetName="Supp Table 4 paths_summary", append=TRUE, row.names=FALSE)
